Mapping Microblogging Posts to Encyclopedia Articles

### 2011-02-22 trunk/lids/twittersearchwrap/paper/paper.tex

System Architecture shown in Figure \ref{fig:arch}.

\begin{figure}[htb]
  \centering
  \includegraphics[width=.6\linewidth]{architecture}
  \caption{System architecture}
  \label{fig:arch}
\end{figure}

>>>>

The implemented system (further called twitter search wrapper) is called with
a query and returns a rdf\footnote{\url{http://www.w3.org/RDF/}} document
describing the most recent twitter posts (further called tweets) matching the
given query. The returned rdf document furthermore contains a mapping of the
query to Wikipedia articles which based on the content published by users that most recently used the query in their
posts maps to articles best describing the content of tweets related to the
query. An overview of the System Architecture is given in Figure \ref{fig:arch}.
In detail, methods performed by the twitter search wrapper can be grouped
and best described in five sequential steps (see Figure \ref{fig:arch}) .

\begin{figure}[htb]
  \centering
  \includegraphics[width=.6\linewidth]{architecture}
  \caption{System Architecture}
  \label{fig:arch}
\end{figure}

In a first step the implemented twitter search wrapper fetches the atom feed
generated by the twitter search
api\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
query. The generated feed contains information about the 100 most recently published publicly visible tweets and
their authors which match the search query. The tweets itself are described by
their content, publishing date, authors and optionally a geographic location.
